Supplemental Materials for: Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-06-02 doc/peakcharacterization_supplemental.Rmd
last set of changes

```{r coefficient_table}
ecf_coef_table = all_models[[1]]$model_data %>%
  flextable() %>%
  colformat_double(digits = 0) %>%
  autofit()
ecf_coef_table
```

@@

```{r peak_variance, dn_id = figure_count, fig.width = 8, fig.height=9}
filtersd_only = rsd_combine %>%
  dplyr::filter(processed %in% "filtersd", n_perc >= 0.9)

@@

sd_by_sample = purrr::map(filtersd_by_sample, function(in_sample){
  mean_sd = in_sample %>%
    ggplot(aes(x = log10(mean), y = sd)) +
    geom_point(alpha = 0.5) +
    labs(subtitle = in_sample$sample[1])
  mean_rsd = in_sample %>%
    ggplot(aes(x = log10(mean), y = rsd)) +
    geom_point(alpha = 0.5)
  mean_sd | mean_rsd
})

@@

compare_sina = lung_compare_corrected %>%
  ggplot(aes(x = compare_id, y = p_diff)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_sina(alpha = 0.5) +
  geom_point(data = long_measure, aes(x = compare_id, y = value), color = "green") +
  geom_text(data = long_pvalue, aes(x = compare_id, y = -1, label = format(value, digits = 2))) +
  labs(x = "", y = "Log-P-Value Difference")

compare_pair = lung_compare_corrected %>%
  ggplot(aes(x = log_p.ref, y = log_p.test)) +
  geom_abline(slope = 1, color = "red") +
  geom_point(alpha = 0.5) +
  labs(x = "Log-P-Value Raw",
         y = "Log-P-Value Corrected")
compare_pair | compare_sina + plot_annotation(tag_levels = "A")
```

>>>>

```{r coefficient_table}
ecf_coef_table = all_models[[1]]$model_data %>%
  flextable() %>%
  colformat_double(digits = 0, big.mark = ",") %>%
  autofit()
ecf_coef_table
```

@@

```{r peak_variance, dn_id = figure_count, fig.width = 8, fig.height=9}
scientific_10 = function(x) {
  gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))
}

scientific_10_label = function(x) {
  parse(text = gsub("e\\+*", " %*% 10^", scales::scientific_format()(x)))
}

filtersd_only = rsd_combine %>%
  dplyr::filter(processed %in% "filtersd", n_perc >= 0.9)

@@

sd_by_sample = purrr::map(filtersd_by_sample, function(in_sample){
  mean_sd = in_sample %>%
    ggplot(aes(x = log10(mean), y = sd)) +
    geom_point(alpha = 0.5) +
    labs(subtitle = in_sample$sample[1]) +
    scale_y_continuous(labels = scientific_10_label)
  mean_rsd = in_sample %>%
    ggplot(aes(x = log10(mean), y = rsd)) +
    geom_point(alpha = 0.5)
  mean_sd | mean_rsd
})

@@

compare_sina = lung_compare_corrected %>%
  ggplot(aes(x = compare_id, y = p_diff)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_sina(alpha = 0.5) +
  geom_point(data = long_measure, aes(x = compare_id, y = value), color = "green") +
  geom_text(data = long_pvalue, aes(x = compare_id, y = -1, label = scientific_10(value)), parse = TRUE) +
  labs(x = "", y = expression(paste("Log-", italic("P"), "-Value Difference", sep = "")))

compare_pair = lung_compare_corrected %>%
  ggplot(aes(x = log_p.ref, y = log_p.test)) +
  geom_abline(slope = 1, color = "red") +
  geom_point(alpha = 0.5) +
  labs(x = expression(paste("Log-", italic("P"), "-Value Raw", sep = "")),
         y = expression(paste("Log-", italic("P"), "-Value Corrected", sep = "")))
(compare_pair | compare_sina) + plot_annotation(tag_levels = "A")
```
